Species turnover reveals hidden effects of decreasing Nitrogen deposition in mountain hay meadows

### 2018-06-18 Manuscript.Rmd
Update Manuscript.Rmd
Literatur ergänzt 
Abb. 2 oligo- und eutrophic species (statt N-Wert)

The average $\pm$ SD percentage of species that differed between replicated surveys was `r mean(100 * turnover_double$turnover)` $\pm$ `r sd(100 * turnover_double$turnover)`. This pseud-turnover was lower than the observed temporal turnover: the average percentage of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seemed that the turnover from the first/second survey to the turnover of the second/third survey moderately decreased (90% Credible interval of the change in turnover estimated from the Binomial generalized linear mixed model: `r CrI`). Variation in species turnover was largest along the Nitrogen deposition gradient with highest species turnover at sites with low Nitrogen deposition (Table \@ref(tab:turnovertab)). The other three gradients were less important to explain the variation in species turnover among sites.

>>>>

The average $\pm$ SD percentage of species that differed between replicated surveys was `r mean(100 * turnover_double$turnover)` $\pm$ `r sd(100 * turnover_double$turnover)`%. This pseud-turnover was lower than the observed temporal turnover: the average percentage of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seemed that the turnover from the first/second survey to the turnover of the second/third survey moderately decreased (90% Credible interval of the change in turnover estimated from the Binomial generalized linear mixed model: `r CrI`). Variation in species turnover was largest along the Nitrogen deposition gradient with highest species turnover at sites with low Nitrogen deposition (Table \@ref(tab:turnovertab)). The other three gradients were less important to explain the variation in species turnover among sites.
